Simulation_Study

### 2022-02-22 Simulation_Study.Rmd
Simulation Study for n = 100

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n, sd = sd)
  bt <- blkboot(x, statistic, 1000, l) 
  nm_interval = c(bt$stat - 1.96*sd(bt$nm.stat), bt$stat + 1.96*sd(bt$nm.stat))
  mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
  if (0.5 >)
  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval) 
    # returns statistics and sd's for nm and mv respectively

@@

Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1

```{r functions, echo = False}
ar1 <- function(x) cor(x[-1], x[-length(x)])
sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, ar1))
print(sim)

>>>>

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n, sd = sd)
  bt <- blkboot(x, statistic, 1000, l) 
  nm_interval = c(bt$stat - 1.96*sd(bt$nm.stat), bt$stat + 1.96*sd(bt$nm.stat))
  mv_interval = c(bt$stat - 1.96*sd(bt$mv.stat), bt$stat + 1.96*sd(bt$mv.stat))
  nm_chi = c(999 * var(bt$nm.stat) / qchisq(p = .025, df = 999, lower.tail = FALSE), 999 * var(bt$nm.stat) / qchisq(p = .975, df = 999, lower.tail = FALSE))
  mv_chi = c(999 * var(bt$mv.stat) / qchisq(p = .025, df = 999, lower.tail = FALSE), 999 * var(bt$mv.stat) / qchisq(p = .975, df = 999, lower.tail = FALSE))
  nm_contains = FALSE
  if (nm_interval[1] < theta && nm_interval[2] > theta)
  {
    nm_contains = TRUE
  }
  mv_contains = FALSE
  if (mv_interval[1] < theta && mv_interval[2] > theta)
  {
    mv_contains = TRUE
  }
  nm_chi_contains = FALSE
  if (nm_chi[1] < sd**2 && nm_chi[2] > sd**2)
  {
    nm_chi_contains = TRUE
  }
  mv_chi_contains = FALSE
  if (mv_chi[1] < sd**2 && mv_chi[2] > sd**2)
  {
    mv_chi_contains = TRUE
  }

  c(bt$stat, sd(bt$nm.stat), sd(bt$mv.stat), nm_interval, mv_interval, nm_contains, mv_contains, nm_chi, mv_chi, nm_chi_contains, mv_chi_contains) 
    # returns statistics and sd's for nm and mv respectively

@@

Let's conduct a simulation study with n = 100, ar = 0.5, and sd = 0.1 (var = 0.01)

```{r functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
nmcount = 0
mvcount = 0
nmchicount = 0
mvchicount = 0
sim <- replicate(100, do1rep(100, 0.7, 0.3, 10, ar1))
print(sim)
for(i in sim[8,])
{
  if(i == 1)
  {
    nmcount = nmcount + 1
  }
}
for(i in sim[9,])
{
  if(i == 1)
  {
    mvcount = mvcount + 1
  }
}
for(i in sim[14,])
{
  if(i == 1)
  {
    nmchicount = nmchicount + 1
  }
}
for(i in sim[15,])
{
  if(i == 1)
  {
    mvchicount = mvchicount + 1
  }
}
c(nmcount, mvcount, nmchicount, mvchicount)
